\begin{abstract}
We present AutoTerm-SST, an interactive system for terminology-aware streaming
speech translation. Live domain talks often contain rare entities, technical
terms, and rapidly changing vocabulary, yet requiring users to prepare a
glossary before a session creates substantial friction. AutoTerm-SST addresses
this problem with a zero-setup adaptive terminology memory: every streaming
chunk receives a fixed list of 10 glossary candidates, while the automatic mode
controls which terminology slices are active and how candidates are ranked into
that fixed budget. A training-free router combines generated target-translation
topic evidence, speech-window domain probes, speech-centroid evidence, and
retrieved-term metadata, without running a separate ASR or source-transcript
classifier in the production path. It selects directly among domain-specific
terminology slices when confidence guards are satisfied. The demo exposes
translations together with retrieved terms, active slices, router decisions, and
retrieval latency in a live evidence panel.
In a terminology smoke evaluation, the zero-setup working glossary recovers
eight of nine gold terms while using a lower-noise active inventory than a broad
100k open memory; separate scale probes show warm MaxSim retrieval remains
within about 60--105 ms p95 up to million-term memories. A mixed-domain routing
probe shows the active glossary following ACL/medicine domain transitions with
no wrong switches. AutoTerm-SST is released as a pluggable RASST-Demo framework
with mock and live GPU modes.
\end{abstract}
