\section{Introduction}

Simultaneous speech translation (SST) targets technical talks, lectures,
meetings, and live media. Prior SST work studies the quality--latency
trade-off of prefix translation \citep{ma2019stacl} and standardizes streaming
evaluation \citep{ma2020simuleval}. Recent omni speech-language models broaden
the available modeling options for long-form speech translation
\citep{xu2025qwen3omni}, but live systems
still struggle with term-dense content: named methods, datasets, clinical terms,
legal phrases, and financial entities often require specialized translations
that are difficult to infer from local acoustic context alone.

Glossaries are a practical way to control terminology, but they are awkward for
live use. A user may not know the exact topic before a talk starts, and asking
every speaker or viewer to upload a domain glossary or select a domain creates
friction. At deployment time, operators register modular, pre-indexed
terminology resources for different domains. At session time, users neither
upload a glossary nor select a domain: AutoTerm-SST maintains a small active
working set from streaming evidence and injects at most 10 retrieved terms into
each LLM prompt. This allows new domains to be added without retraining the
translation model or collapsing all terminology resources into a single
monolithic inventory.

AutoTerm-SST treats terminology control as an active-inventory and ranking
problem. RASST uses glossary retrieval to expose out-of-distribution terms to
the language model, but the retriever and prompt have finite ranking capacity:
as a universal glossary grows, more irrelevant and conflicting references
compete for the same evidence budget. AutoTerm adds a cache-like management
layer above the unchanged retriever. Semantic similarity admits promising
slices, the current slice receives recency-style pinning, and low-priority
slices leave the working set when its term budget is full. The motivation is
not that million-term retrieval is computationally infeasible, but that a small
active set remains more relevant as the offline catalog expands.

The result is an interactive streaming SST workbench rather than a new
translation model. The framework handles REST/WebSocket transport, session
lifecycle, and agent routing; agents handle model inference, prompting,
batching, and retrieval. The live agent uses Qwen3-Omni with vLLM continuous
batching \citep{kwon2023efficient}, and the web and Electron interfaces expose
retrieved terms, active glossary status, router decisions, and latency alongside
translations.

Our contributions are:
\begin{itemize}
    \item We build AutoTerm-SST, a pluggable streaming SST demo with a live
    evidence panel for retrieved terminology, active glossary state, router
    decisions, and latency.
    \item We introduce zero session-time terminology setup: users neither
    upload a glossary nor select a domain, while a training-free, budgeted
    active-slice cache keeps multiple plausible topic glossaries available.
    \item On a complete ten-talk stream, we compare the working set with nested
    100k/1M merged glossaries and a known-domain reference, alongside retrieval
    scale and 32-session concurrent serving.
\end{itemize}
