\section{Related Work}

\paragraph{Streaming speech translation.}
SST systems must translate partial speech while balancing quality and latency. Prefix-to-prefix policies such as wait-\(k\) make this trade-off explicit \citep{ma2019stacl}, attention-based policies refine read/write decisions \citep{papi2023alignatt,papi2024streamatt}, SimulEval standardizes evaluation \citep{ma2020simuleval}, and large-scale streaming models target direct simultaneous translation \citep{seamless2023,zhang2024streamspeech}. Speech language models make this setting more flexible \citep{xu2025qwen3omni,ouyang2025infinisst}, but live deployment still requires session management, incremental transport, and latency-aware prompting. Unlike existing streaming ST demonstrators, which fix vocabulary context at session start, AutoTerm-SST manages terminology \emph{during} the stream, as a system demonstration rather than a new architecture.

\paragraph{Terminology-aware translation.}
Terminology control has long been studied in machine translation, usually through user-provided dictionaries, constrained decoding, or training-time exposure to terminology constraints \citep{hokamp2017lexically,dinu2019training}; terms and named entities are also a known weak point of speech translation specifically \citep{gaido2021moby}. Retrieval-augmented generation offers another way to expose non-parametric memory at generation time \citep{lewis2020retrieval,khandelwal2021nearest}. These methods assume the domain is known ahead of time. RASST couples a speech-side MaxSim retriever with prompt-injected terminology \citep{luo2026rasst}; AutoTerm-SST builds on it with a zero-setup interaction pattern, maintaining the active terminology context from retrieval evidence observed during streaming.

\paragraph{LLM serving and demo systems.}
Modern LLM serving systems provide continuous batching and efficient generation APIs \citep{kwon2023efficient,zheng2024sglang}, but a streaming speech demo also needs microphone/file input, WebSocket transport, session cleanup, live evidence rendering, and mock-mode testing. Translation Canvas \citep{dandekar2024translation} targets offline translation analysis; AutoTerm-SST contributes the live serving layer, keeping model-specific code inside swappable agents.
