\section{System Overview}
\label{sec:system}

AutoTerm-SST is organized as a thin framework plus swappable translation agents
(Figure~\ref{fig:architecture}). The framework is deliberately small: it serves
the web UI, accepts REST control requests, streams audio over WebSockets, tracks
session lifecycle, and routes each session to an agent selected by
\texttt{agent\_type}. The framework does not know about model prompts,
retrieval, batching, KV cache, or glossary construction.

\begin{figure}[t]
\centering
\fbox{\begin{minipage}{0.96\columnwidth}
\centering
\textbf{Client} \(\rightarrow\)
\textbf{Thin Framework} \(\rightarrow\)
\textbf{Agent Boundary}

\vspace{0.4em}
\begin{tabular}{p{0.27\columnwidth}p{0.30\columnwidth}p{0.27\columnwidth}}
\centering Web / Electron &
\centering REST, WebSocket, session routing &
\centering OmniAgent / mock
\tabularnewline
\end{tabular}

\vspace{0.6em}
\hrule
\vspace{0.6em}
\textbf{Inside OmniAgent:}
audio buffer + micro-batcher \(\rightarrow\)
retrieval plugin \(\rightarrow\)
audio-native router \(\rightarrow\)
PromptBuilder \(\rightarrow\)
Qwen3-Omni/vLLM backend

\vspace{0.4em}
\textbf{Output:} translation text + retrieved terms + active glossary metadata
\end{minipage}}
\caption{AutoTerm-SST separates transport/session logic from model-specific agent logic. Retrieval, active glossary routing, prompting, and vLLM generation all live inside the agent boundary.}
\label{fig:architecture}
\end{figure}

\paragraph{Agent contract.}
Agents implement a small contract: \texttt{open\_session},
\texttt{submit\_audio}, \texttt{on\_control}, \texttt{close\_session},
\texttt{describe}, and \texttt{health}. This lets the same UI and wire protocol
serve a deterministic mock agent for development, a legacy InfiniSST scheduler
agent, or the RASST/Qwen3-Omni agent used in the live GPU demo.
The agent boundary is backend-agnostic: the current live demo uses in-process
vLLM \citep{kwon2023efficient}, while the same protocol can connect to external
SGLang-compatible serving backends without changing the terminology memory,
router, or UI.

\paragraph{Streaming agent.}
For each audio chunk, the OmniAgent can run MaxSim terminology retrieval over
the active slices, build a \texttt{term\_map}, and call the in-process vLLM
backend. In \texttt{auto\_working}, the retriever returns up to 10 ranked
glossary candidates and filters low-confidence matches before the PromptBuilder
constructs the prompt.
The agent emits partial translations plus structured metadata, including
retrieved terms, retrieval latency, active slices, prompt-reference counts, and
router decisions.

\paragraph{Evidence protocol.}
The default WebSocket output remains plain text for backward compatibility. A
JSON mode returns \texttt{\{type, text, meta\}}, where \texttt{meta.references}
drives the live evidence panel and \texttt{meta.topic} /
\texttt{meta.topic\_router} describe the adaptive glossary state. This evidence
protocol is central to the demo: users can see which terms were retrieved and
whether the router stayed, switched, or deferred a glossary change.
