\section{Adaptive Terminology Memory}
\label{sec:adaptive-memory}

AutoTerm separates the broad offline catalog from the compact glossary exposed
to a live session. Each topic slice contains term--translation pairs, a
prebuilt MaxSim index, and a bilingual prototype formed from a short topic
description and representative terminology. Domain-dependent mappings are
retained: the same source term may have different translations in different
slices.

\paragraph{Offline catalog registration.}
An operator registers each slice through a manifest containing its label, term
count, prototype, and prebuilt index. Slices are independently replaceable;
topic-dependent mappings remain separate. At session time the router reads the
compact manifest and prototypes, while indexes outside the working set do not
participate in retrieval. Catalog capacity is thereby separated from the
terminology exposed to one decoding step.

\paragraph{Semantic routing.}
At chunk $t$, the router concatenates the most recent $w$ generated
translation chunks into context $c_t$. For slice $d$ with prototype examples
$P_d$ and multilingual sentence encoder $E$, it computes
\begin{equation}
\begin{aligned}
  \bar p_d &=
  \operatorname{norm}\!\left(\frac{1}{|P_d|}
  \sum_{p\in P_d} E(p)\right), \\
  s(d\mid c_t) &= \cos\!\left(E(c_t),\bar p_d\right).
\end{aligned}
\end{equation}

\begin{table*}[t]
\centering
\footnotesize
\setlength{\tabcolsep}{3.5pt}
\begin{tabular}{llrrrrrrrr}
\toprule
Setting & Input & Active & \multicolumn{3}{c}{TERM\_ACC (\%)} & BLEU & MT-BLEU & Prec. (\%) & Refs \\
\cmidrule(lr){4-6}
& & & NLP & Med. & All & & & & \\
\midrule
InfiniSST (no RAG) & None & 0 & 76.6 & 46.3 & 61.4 & 41.84 & 38.32 & 0.0 & 0.00 \\
Known-domain-1k & Domain & 1k & 88.8 & \textbf{86.6} & \textbf{88.1} & \textbf{45.19} & \textbf{42.39} & \textbf{48.7} & \textbf{0.69} \\
AutoTerm-1k$\times$4 & None & $\leq$4k & 89.3 & 86.3 & \textbf{88.3} & 45.09 & 42.28 & 34.8 & 0.94 \\
Merged-100k & None & 100k & \textbf{89.4} & 84.5 & 87.8 & 43.72 & 40.93 & 6.8 & 4.96 \\
Merged-1M & None & 1M & 87.1 & 78.9 & 84.4 & 42.79 & 39.95 & 3.4 & 8.70 \\
\bottomrule
\end{tabular}
\caption{Ten-talk comparison under a fixed retrieval/prompt budget. BLEU and
MT-BLEU use StreamLAAL-compatible mWER resegmentation. The four RAG rows share
2,047 raw-term occurrences (1,368 NLP; 679 medicine). InfiniSST reports the
canonical LM=2 five-talk scores; its All/BLEU/MT-BLEU are two-corpus macro
means. Prec. is prompt precision; no RAG injects no references.}
\label{tab:quality}
\end{table*}

We use BGE-M3 for $E$. Prototypes contain a short bilingual description and
representative terms, so Chinese generated context and English topic metadata
share one embedding space. The routing path is therefore a direct semantic
similarity computation over accumulated translation context, not a classifier
trained on the evaluation talks.

\paragraph{Why generated target context?}
The speech-language model translates audio directly, without a stable source
transcript. Its partial target text is already available and becomes more
topic-specific over time, enabling comparison with bilingual prototypes
without a supervised domain model. Routing is causal: chunk $t$ only changes
later retrieval. A generic early translation can therefore delay topic
evidence; accumulating four chunks and retaining several slices makes this
signal less brittle.

The highest-scoring slices are admitted until either the maximum slice count
$K$ or total active-term budget $B$ is reached. The current best slice is
pinned when possible to reduce oscillation. Keeping multiple plausible slices
is important: a temporary top-1 routing error need not remove the correct
terminology from retrieval.

\paragraph{Working-set update.}
At each routing tick, AutoTerm keeps the current slice if it fits, then fills
remaining slots in similarity order. Lower-ranked non-pinned slices stay
outside the budget. This cache-like rule is not a hard domain switch: plausible
topics can coexist during a transition, while stale slices disappear as their
scores fall. Candidate indexes are preloaded and selections change only
between decoding steps.

\paragraph{Fixed evidence budget.}
All active slices share a top-100 returned-candidate budget and a common top-10
prompt cap. Increasing $K$ therefore changes the composition of the search
space, not the amount of evidence available to AutoTerm. In the evaluated
configuration, the router considers ten 1k slices, uses the latest four translation chunks,
and activates at most four slices ($B{=}4{,}000$). The known-domain reference
searches the matching 1k slice; universal baselines search nested 100k and 1M
indexes under exactly the same retrieval and prompt limits.

For a multi-slice query, the system divides the 100 candidate slots among the
active indexes, combines their results, removes only exact duplicate
source--target pairs, and globally reranks the remaining candidates before the
top-10 prompt cap. Consequently, selecting four slices does not give AutoTerm
four times the retrieval or prompt capacity. Its advantage can only come from
placing more relevant mappings inside the same evidence budget.

The context encoder scores all lightweight prototypes together, and likely
indexes are warmed asynchronously. Each chunk retrieves from a snapshot of the
working set installed before that chunk began; a routing update that finishes
during generation only affects the next chunk. This keeps terminology evidence
causal and prevents cold index loading from changing an in-flight prompt.

The million-entry baseline is a capacity stress condition, not a claim that
large-index search is computationally impossible. AutoTerm addresses a
different problem: preserving relevant prompt evidence as an offline catalog
grows, without requiring any session-time input from the user.
