\section{Evaluation}
\label{sec:evaluation}

\paragraph{Setup.}
We evaluate the terminology-memory behavior of the live AutoTerm-SST framework
on Taurus A6000 GPUs. The RASST agent runs Qwen3-Omni with in-process vLLM
tensor parallelism over two GPUs and a MaxSim retriever on a third GPU. Audio is
from ACL6060 English-to-Chinese prepared segments. Unless otherwise stated,
results use the framework JSON WebSocket protocol, which exposes translated
text, retrieved references, active glossary metadata, and per-chunk retrieval
latency.

\paragraph{Metrics.}
For terminology quality, we report term accuracy over an independent 9-term gold
set for the smoke talk \texttt{2022.acl-long.268}. Masked BLEU removes
target-side glossary translations from both hypothesis and reference; we use it
only as a non-terminology sanity check, not as the primary glossary metric. For
runtime, we report retrieved references per partial chunk and retrieval latency
percentiles. A separate SimulEval-compatible stress run measures end-to-end
streaming quality/latency for the base streaming system \citep{ma2020simuleval};
the glossary table should be read as terminology and retrieval evidence, not as
a replacement for token-delay StreamLAAL.

\begin{table}[t]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lcrrrrr}
\toprule
Setting & Effort & Terms & Term acc. & M-BLEU & Refs & p95 \\
\midrule
None & 0 & 0 & 0.444 & 42.34 & 0.00 & -- \\
Broad open & 0 & 100k & 0.444 & 45.29 & 5.03 & 111.54 \\
Auto working & 0 & 10k & \textbf{0.889} & 45.80 & 2.29 & 88.20 \\
Curated ACL & high & 238 & 0.778 & \textbf{47.07} & 1.94 & 81.13 \\
\bottomrule
\end{tabular}}
\caption{Terminology smoke evaluation on the first eight audio segments of
\texttt{2022.acl-long.268}, streamed as 31 JSON partial chunks. M-BLEU is
masked BLEU; Refs is retrieved references per chunk; p95 is retrieval latency in
ms. The zero-setup \texttt{auto\_working} setting improves 9-term accuracy while
injecting fewer references than the broad 100k memory.}
\label{tab:quality}
\end{table}

\paragraph{Terminology usefulness.}
Table~\ref{tab:quality} compares four user-facing settings. Broad open memory is
zero-effort, but it retrieves more low-precision candidates without improving
term accuracy on this slice. The adaptive working glossary keeps the same zero
user effort while selecting candidates from the configured domain-specific
active inventory; it recovers eight of nine gold terms and reduces retrieval p95
relative to the broad 100k memory. The curated
ACL glossary has the best masked BLEU and lowest retrieval latency, but it
requires a manually curated domain glossary. Importantly, this short smoke clip
does not demonstrate a domain switch: the \texttt{auto\_working} run stays on
the configured initial domain slice because the router's confidence and interval
guards do not activate another domain slice. We therefore frame Table~\ref{tab:quality} as
evidence for compact zero-setup working memory, while the interface exposes
switch decisions and guard reasons for longer or clearer-domain sessions.

\begin{table}[t]
\centering
\scriptsize
\begin{tabular}{lrrr}
\toprule
Memory & Terms & p50/p95 ms & Refs/chunk \\
\midrule
Curated & 238 & 61.3 / 105.3 & 2.33 \\
Domain & 10k & 78.5 / 82.1 & 1.80 \\
Open & 100k & 64.1 / 82.6 & 4.89 \\
Stress & 1M & 78 / 95 & 9.62 \\
\bottomrule
\end{tabular}
\caption{Warm steady-state MaxSim retrieval latency across terminology memory
sizes. Cold loading grows with index size (about 0.5s for 238 terms, 6.8s for
100k, and over 30s for 1M), so AutoTerm-SST preloads candidate working indexes
outside the streaming batch path.}
\label{tab:scale}
\end{table}

\paragraph{Scale and prompt noise.}
Table~\ref{tab:scale} shows that warm MaxSim retrieval remains near 60--105 ms
p95 from curated glossaries to million-term memories. The bottleneck is not
per-chunk exact retrieval; it is cold index loading and reference noise. As
memories grow, refs/chunk increases, so the prompt receives more distractor
terms even when useful terms remain retrievable. This supports the central
design choice: keep the live active glossary compact and treat large open memory
as an offline resource pool and stress test.

\paragraph{Concurrent streaming.}
In a separate SimulEval-compatible 32-session stress run, the framework produced
BLEU 47.38, StreamLAAL 2264 ms, and StreamLAAL-CA 2265 ms over ACL6060 with a
merged \texttt{instances.log}. This result validates the streaming transport and
agent serving path under concurrent use. It is not a glossary ablation, so we do
not mix it into Table~\ref{tab:quality}; instead, it provides system evidence
that the demo can sustain multi-session streaming while the terminology
evaluation isolates active-memory behavior.
