\section{Limitations and Conclusion}
\label{sec:limitations}

AutoTerm-SST is a terminology-aware streaming system, not a new foundation
model or an open-world topic classifier. Semantic routing depends on short
offline slice descriptions and bilingual prototypes; a novel or ambiguous
topic may therefore receive a poor working set. Because the strongest routing
evidence is recent generated translation, the pinned slice can lag after a
domain boundary, although activating several slices reduces the cost of a
single wrong top-1 choice. The main comparison covers one En$\rightarrow$Zh
ten-talk stream and ten candidate slices. The registered 1k slices contain the
benchmark terminology, so this is a controlled routing and ranking result, not
a held-out test of glossary induction. It is also
not evidence that every million-entry glossary or language pair will degrade by
the same amount. In particular, Merged-100k remains usable and the controlled
ACL sweep stays stable through 100k, while a 1M MaxSim index is
computationally usable; the observed failure is ranking and prompt crowding
under a fixed evidence budget. The hosted live backend also
requires A6000-class NVIDIA GPUs and external model/retriever artifacts, while mock
mode covers UI and protocol testing without them.

We presented AutoTerm-SST, which removes per-session glossary upload and domain
selection by routing a compact multi-slice working glossary from streaming
context. On the complete ten-talk comparison, this working set matches the
known-domain reference and improves term and translation quality over both
merged baselines while injecting substantially cleaner prompt evidence. The
architecture also provides a practical expansion
path: new topic slices can be registered offline without forcing every session
to search one ever-growing universal glossary.
