\appendix

\section{Router Configuration and Guards}
\label{app:router}

Table~\ref{tab:router-config} lists the default production configuration of
the hybrid active-glossary router as released in
\texttt{configs/autoterm\_slices.yaml}; deployment-specific configurations can
override individual values explicitly. Guards are evaluated in order: warmup,
update interval, target-equals-active, index readiness, probe floors,
confidence, top-vs-runner-up margin, target-vs-current margin, post-switch
cooldown, and consecutive-window consistency. Uncertain windows keep the
current slice. The released configuration uses two consistent generated-target
windows and a 0.30 target-vs-current margin; the two 640-window proxy tests in
Section~\ref{sec:evaluation} used three generated-target windows.

The weights are hand-set on the proxy schedules, not fitted to the audio
evaluation runs. A proxy weight sweep (\(\lambda_t\) from 0.25 to 0.80,
including dropping the centroid and metadata terms) leaves switching
unchanged: every mixed-signal configuration completes all 16
alternating/random transitions with zero wrong switches, at a latency fixed
by the three-window consistency guard. Setting \(\lambda_t{=}1\) (no probe
channel) blocks most switches (1/9 and 2/7), so the speech probe is a
required corroborating guard even though it is too noisy to lead
(Section~\ref{sec:evaluation}).

\begin{table}[ht]
\centering
\small
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lr}
\toprule
Parameter & Default \\
\midrule
\multicolumn{2}{l}{\emph{Signal weights (renormalized per window)}} \\
\quad generated-target topic \(\lambda_t\) & 0.60 \\
\quad speech-window domain probe \(\lambda_p\) & 0.25 \\
\quad speech centroid \(\lambda_c\) & 0.10 \\
\quad reference metadata \(\lambda_m\) & 0.05 \\
\midrule
\multicolumn{2}{l}{\emph{Switch thresholds}} \\
\quad activation confidence & 0.60 \\
\quad top-vs-runner-up margin & 0.15 \\
\quad target-vs-current margin & 0.30 \\
\quad consistent windows (text / gen.\ target / audio) & 2 / 2 / 3 \\
\midrule
\multicolumn{2}{l}{\emph{Audio-probe floors / schedule / retrieval}} \\
\quad probe top score / margin / positive domains & 0.50 / 0.08 / 2 \\
\quad warmup / update / cooldown / staleness & 20s / 10s / 30s / 120s \\
\quad cap \texttt{PROMPT\_K} / score threshold & 10 / 0.78 \\
\bottomrule
\end{tabular}}
\caption{Released hybrid-router defaults. Signal weights are renormalized
over the signals present in each window; the three consistent-window counts
apply per evidence path (manifest text / generated target / audio-only).}
\label{tab:router-config}
\end{table}

\section{Glossary-Scale Streaming Sweep}
\label{app:sweep}

\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{lrrr}
\toprule
Memory & Terms & p50/p95 ms & Refs/chunk \\
\midrule
Curated & 238 & 61.3 / 105.3 & 2.33 \\
Domain & 10k & 78.5 / 82.1 & 1.80 \\
Open & 100k & 64.1 / 82.6 & 4.89 \\
Stress & 1M & 78 / 95 & 9.62 \\
\bottomrule
\end{tabular}
\caption{Warm per-chunk MaxSim retrieval latency (p50/p95) and surviving
prompt references per chunk (Refs) by memory size. The cost that scales is
cold index loading (0.5s at 238 terms, 6.8s at 100k, over 30s at 1M), which
AutoTerm-SST does off the streaming path.}
\label{tab:scale}
\end{table}

Table~\ref{tab:sweep} reports the five-talk streaming sweep referenced in
Section~\ref{sec:evaluation}: five concatenated ACL 60-60 talks (3{,}442s of
audio) streamed through the live JSON WebSocket at latency multiplier 2, scored
against a curated 142-term technical gold set. Each inventory always contains
the full 238-entry curated ACL glossary; larger rows add Wikidata-mined AI/CS
candidates as distractors. These are manual-preset runs isolating inventory
scale (not \texttt{auto\_working} runs). Term accuracy, BLEU, and masked
BLEU stay in a narrow band up to 100k terms while retrieval precision
collapses, motivating compact routed active slices.

\begin{table}[ht]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lrrrrrrr}
\toprule
Inventory & Terms & Term acc. & BLEU & M-BLEU & Gold@10 & Prec@10 & Refs \\
\midrule
Curated ACL & 238 & 0.972 & 58.27 & 53.10 & 0.972 & 0.480 & 1.53 \\
+AI transl.\ 10k & 10{,}238 & 0.965 & 58.72 & 53.35 & 0.972 & 0.234 & 3.09 \\
+AI broad 10k & 10{,}238 & 0.972 & 58.38 & 52.75 & 0.979 & 0.367 & 2.00 \\
+AI broad 50k & 50{,}238 & 0.979 & 58.65 & 53.24 & 0.979 & 0.196 & 3.64 \\
+AI broad 100k & 100{,}238 & 0.965 & 58.83 & 53.32 & 0.979 & 0.137 & 5.03 \\
\bottomrule
\end{tabular}}
\caption{Five-talk streaming sweep (latency multiplier 2) against the
142-term technical gold set. Gold@10 = fraction of gold terms surfaced within
the top-10 prompt cap; Prec@10 = retrieval precision at 10; Refs = surviving
prompt references per chunk; M-BLEU = BLEU after deleting gold term strings
from hypothesis and reference. At latency multiplier 1 the pattern holds
(term accuracy 0.944--0.958; precision 0.479 \(\rightarrow\) 0.133).}
\label{tab:sweep}
\end{table}

\section{Mixed-Domain Terminology under Union Inventories}
\label{app:mixed}

A glossary-channel comparison is only meaningful when the gold terms are
inside the retrieval inventory: the broad wiki slices cover 29/142 of the ACL
technical gold and 1/54 of the \texttt{medicine\_606} gold, so their term
accuracy mostly measures base-model retention. We therefore evaluate with
\emph{benchmark-aligned union inventories} at a fixed 10k inventory size: the
byte-identical gold glossary (238 ACL / 212 hard-medicine terms) plus
seeded wiki fillers, mirroring the recipe of Appendix~\ref{app:sweep}
(gold coverage 142/142 and 54/54).

Table~\ref{tab:mixed} gives the full detail for the ten-talk run of
Table~\ref{tab:quality} (five ACL and five medicine talks alternating,
16,848s streamed live in real time through one session): raw-gold and
type-level term accuracy plus masked BLEU. Automatic mode requires no
session-time glossary input or domain choice but relies on inventories built
offline. All nine domain transitions switch in the correct direction with one
transient extra switch (steady-state active-domain accuracy 0.982); eight of
nine switches land within 13.6--55.4s, and one delayed medicine-to-ACL switch
takes 304s over a generic talk opening. A truncated three-block probe
(ACL\,$\rightarrow$\,medicine\,$\rightarrow$\,ACL, 600s per block) shows the
same ordering --- Automatic 0.909/0.907 combined versus 0.818/0.854 (fixed
NLP) and 0.811/0.810 (fixed medicine), with switches 37.4s/25.0s after the
boundaries --- and a gold-only 212-term medicine inventory without fillers
reaches just 0.790, confirming that compact curated slices need distractor
mass to be a realistic comparison.

\begin{table}[ht]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lrrrrrrr}
\toprule
Setting & Acc\textsubscript{tech} & Acc\textsubscript{raw} & ACL & Med. & Med.\ types & BLEU & M-BLEU \\
\midrule
None & 0.659 & 0.684 & 0.782 & 0.625 & 92/196 & 58.84 & 57.46 \\
Fixed NLP & 0.674 & 0.720 & 0.907 & 0.609 & 86/196 & 59.18 & 57.85 \\
Fixed medicine & 0.863 & 0.850 & 0.772 & 0.889 & 168/196 & \textbf{59.63} & 57.53 \\
Automatic & \textbf{0.905} & \textbf{0.908} & \textbf{0.912} & \textbf{0.903} & \textbf{170/196} & 58.10 & 56.22 \\
\bottomrule
\end{tabular}}
\caption{Full detail for the ten-talk run.
Acc\textsubscript{tech}/Acc\textsubscript{raw} = term accuracy under the
curated technical gold (875 occurrences) and the raw annotation gold
(1{,}064); ACL/Med.\ = per-domain accuracy under the technical gold;
Med.\ types = medicine term types hit at least once (of 196); M-BLEU as in
Table~\ref{tab:sweep}.}
\label{tab:mixed}
\end{table}

\section{\texorpdfstring{Multilingual Terminology (En\,$\rightarrow$\,Ja/De)}{Multilingual Terminology (En to Ja/De)}}
\label{app:multilingual}

The terminology resources provide three target-language translations: the gold
glossaries carry zh/ja/de values, a single MaxSim index serves every target
language (translations are resolved from the term list at prompt time), and the
language pair selects the per-language demo model. Table~\ref{tab:jade} repeats
the mixed
full-length ACL\,$\rightarrow$\,medicine\,$\rightarrow$\,ACL comparison for
En$\rightarrow$Ja and En$\rightarrow$De. Automatic routing, with no
session-time glossary input, has the best combined term accuracy in Japanese
under both gold denominators; in German it leads under the raw gold and
trails the fixed-medicine expert by 1.1 points under the technical gold.
Both languages show zero wrong switches and steady-state active-domain
accuracy 1.0. With the
released ja/de topic keywords, switches land within 29--52s
(ja 28.9/33.5s; de 52.0/33.5s; zh 37.4/25.0s). An ablation without
language-tuned keywords degrades first-switch latency to 115.3s (ja) and
875.6s (de), when routing leans on the slower probe channel. These delays
coincide with lower medicine coverage and BLEU while switch directions stay
correct; the keyword
lists are small, high-precision regex sets per domain. German term matching is
casefolded with light stem tolerance (exact matching undercounts under
inflection); short variants keep strict word boundaries. The medicine
references differ in provenance: German uses human reference translations,
whereas Chinese and Japanese medicine references are model-generated (the ACL
segments use the shared-task human references in all three). Under the
human-referenced German setting, automatic routing still leads on the raw
gold and stays within 1.1 points of the in-domain expert on the technical
gold without any session-time setup.

\begin{table}[ht]
\centering
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llrrrrrrr}
\toprule
 & Setting & Acc\textsubscript{tech} & Acc\textsubscript{raw} & ACL & Med. & Med.\ types & BLEU & M-BLEU \\
\midrule
\multirow{4}{*}{Ja}
 & None & 0.635 & 0.669 & 0.730 & 0.578 & 25/53 & 43.55 & 41.60 \\
 & Fixed NLP & 0.643 & 0.703 & 0.900 & 0.488 & 21/53 & 44.19 & 42.21 \\
 & Fixed medicine & 0.827 & 0.811 & 0.720 & \textbf{0.892} & \textbf{48/53} & \textbf{44.90} & \textbf{42.83} \\
 & Automatic & \textbf{0.857} & \textbf{0.860} & \textbf{0.930} & 0.813 & 43/53 & 39.68 & 37.67 \\
\midrule
\multirow{4}{*}{De}
 & None & 0.653 & 0.669 & 0.740 & 0.604 & 24/49 & 37.52 & 37.47 \\
 & Fixed NLP & 0.667 & 0.694 & 0.840 & 0.571 & 23/49 & 37.21 & 36.91 \\
 & Fixed medicine & \textbf{0.812} & 0.790 & 0.670 & \textbf{0.890} & \textbf{43/49} & \textbf{37.63} & \textbf{37.18} \\
 & Automatic & 0.801 & \textbf{0.795} & \textbf{0.880} & 0.758 & 38/49 & 35.90 & 35.37 \\
\bottomrule
\end{tabular}}
\caption{En$\rightarrow$Ja/De mixed-domain comparison; columns as in
Table~\ref{tab:mixed} (ja: 266/350 technical/raw gold occurrences, 53
medicine types; de: 282/366, 49). All runs use the released configuration
with the ja/de topic keywords.}
\label{tab:jade}
\end{table}
